Evolving Dynamics: The U.S. Labor Force from 1972 to 2022

### 2024-03-17 paper/paper.qmd
fix figure titles and labels

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
fehire_data_long <- fehire_data |>
  pivot_longer(cols = c(strongly_agree, agree, disagree, strongly_disagree),
               names_to = "Response",
               values_to = "Count") |>
  mutate(Count = as.numeric(Count))

# fehire line graph
ggplot(fehire_data_long, aes(x = year, y = Count, group = Response, color = Response)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 1000)) +
  labs(title = "Fehire Responses Over Time",
       x = "Year",
       y = "Count",
       color = "Response Category") +
  theme_minimal()
```

## Attitudes Towards Hiring and Promoting Women
@fig-fehire describes the GSS data on attitudes towards hiring and promoting women from 1996 to 2022, showing a progressive shift towards more positive attitudes. The proportion of respondents strongly agreeing with the need to hire and promote women has seen a significant increase, particularly noticeable in the year 2021, where 620 respondents strongly agreed, compared to 244 in 1996. This trend mirrors a growing consensus on the importance of gender equality in the workplace described by @eagly2020gender, as gender stereotypes have changed. Despite this positive shift, there remains a consistent portion of respondents who disagree to varying degrees, highlighting that there is still work to be done to achieve universal acceptance of this principle.

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
fefam_data_long <- fefam_data |>
  pivot_longer(cols = c(strongly_agree, agree, disagree, strongly_disagree),
               names_to = "Responses",
               values_to = "count") |>
  mutate(count = as.numeric(count))

@@

```{r}
#| label: fig-discaffw
#| fig-cap: Perceptions of Discrimination Against Women in Job Promotions
#| echo: false
#| warning: false
#| message: false

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
discaffw_data_long <- discaffw_data |>
  pivot_longer(cols = c(very_likely, somewhat_likely, somewhat_unlikely, very_unlikely),
               names_to = "Response",
               values_to = "Count") |>
  mutate(Count = as.numeric(Count))

# discaffw line graph
ggplot(discaffw_data_long, aes(x = year, y = Count, group = Response, color = Response)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 700)) +
  labs(title = "Discaffw Responses Over Time",
       x = "Year",
       y = "Count",
       color = "Response Category") +
  theme_minimal()
```

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
education_data_long <- education_data |>
  pivot_longer(cols = c(less_than_highschool, high_school, junior_college, bachelor, graduate),
               names_to = "Education Level",
               values_to = "Count") |>
  mutate(Count = as.numeric(Count))

@@

# combined education and full-time data in line graph
ggplot(combined_data, aes(x = as.numeric(as.character(year)), y = Count, color = category, group = category)) +
  geom_line() +
  scale_y_continuous(name = "Count", limits = c(0, 1000)) +
  labs(title = "Comparison of Full-Time Work for Women with Higher Education Levels",
       x = "Year",
       y = "Count",
       color = "Category") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

library(tidyverse)
library(ggplot2)
library(readxl)
library(tidyr)
library(stringr)

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
fehire_data_long <- fehire_data |>
  pivot_longer(cols = c(strongly_agree, agree, disagree, strongly_disagree),
               names_to = "Response",
               values_to = "Count") |>
  mutate(Count = as.numeric(Count), 
         `Response` = str_replace_all(`Response`, "_", " "),
         `Response` = tools::toTitleCase(`Response`))

# fehire line graph
ggplot(fehire_data_long, aes(x = year, y = Count, group = Response, color = Response)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 1000)) +
  labs(title = "Hiring and Promoting Women: Survey Responses Over Time",
       x = "Year",
       y = "Count",
       color = "Response Category") +
  theme_minimal()
```

## Attitudes Towards Hiring and Promoting Women
@fig-fehire describes the attitudes towards hiring and promoting women from 1996 to 2022, showing a progressive shift towards more positive attitudes. The proportion of respondents strongly agreeing with the need to hire and promote women has seen a significant increase, particularly noticeable in the year 2021, where 620 respondents strongly agreed, compared to 244 in 1996. This trend mirrors a growing consensus on the importance of gender equality in the workplace described by @eagly2020gender, as gender stereotypes have changed. Despite this positive shift, there remains a consistent portion of respondents who disagree to varying degrees, highlighting that there is still work to be done to achieve universal acceptance of this principle.

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
fefam_data_long <- fefam_data |>
  pivot_longer(cols = c(strongly_agree, agree, disagree, strongly_disagree),
               names_to = "Responses",
               values_to = "count") |>
  mutate(count = as.numeric(count), 
         `Responses` = str_replace_all(`Responses`, "_", " "),
         `Responses` = tools::toTitleCase(`Responses`))

@@

```{r}
#| label: fig-discaffw
#| fig-cap: Perceptions of c in Job Promotions
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(ggplot2)
library(readxl)
library(tidyr)
library(stringr)

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
discaffw_data_long <- discaffw_data |>
  pivot_longer(cols = c(very_likely, somewhat_likely, somewhat_unlikely, very_unlikely),
               names_to = "Response",
               values_to = "Count") |>
  mutate(Count = as.numeric(Count), 
         `Response` = str_replace_all(`Response`, "_", " "),
         `Response` = tools::toTitleCase(`Response`))

# discaffw line graph
ggplot(discaffw_data_long, aes(x = year, y = Count, group = Response, color = Response)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 700)) +
  labs(title = "Discrimination Against Women: Survey Responses",
       x = "Year",
       y = "Count",
       color = "Response Category") +
  theme_minimal()
```

@@

# Reshape the data to long format for line graphs and convert 'count' to numeric
education_data_long <- education_data |>
  pivot_longer(cols = c(less_than_highschool, high_school, junior_college, bachelor, graduate),
               names_to = "Education Level",
               values_to = "Count") |>
  mutate(Count = as.numeric(Count), 
         `Education Level` = str_replace_all(`Education Level`, "_", " "),
         `Education Level` = tools::toTitleCase(`Education Level`))

@@

# combined education and full-time data in line graph
ggplot(combined_data, aes(x = as.numeric(as.character(year)), y = Count, color = category, group = category)) +
  geom_line() +
  scale_y_continuous(name = "Count", limits = c(0, 1000)) +
  labs(title = "Women's Full-Time Work and Higher Education Levels",
       x = "Year",
       y = "Count",
       color = "Category") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
